\begin{center}
 VITA
\end{center}

\medskip

\begin{center}
EDUCATION
\end{center}


\begin{flushleft}
\begin{tabular}{ll}
% 2017 - 2020 &  M.S., Astronomy\\
%  & New Mexico State University\\
%  & Las Cruces, New Mexico, USA\\
%  % include the above if you got your MS
 
2015 - 2019 &  B.A., Astrophysics with Honors \\
 & Columbia University \\
 & New York, NY, USA
\end{tabular}
\end{flushleft}

\medskip

\singlespace

\medskip

\begin{center}
FIELD OF STUDY
\end{center}
\begin{flushleft}
Major Field: High Energy Gravitational and Electromagnetic Wave Transients
\end{flushleft}

\begin{center}
PUBLICATIONS % underline your name in the author list of any publications or conference proceedings
\end{center}

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{AGN Disks as Supernova Mufflers II: Radiative Transfer Models}. 2026. (\textit{in prep for the Astrophysical Journal}).

\hangindent=0.5in \noindent E. M. McPike, R. Perna, K.E. S. Ford, B. McKernan, V. Delfavero, \underline{H. E. Cook}, M. McCarthy, K. Nathaniel, J. Postiglione, N. Posner, V. Pritmani, S. Ray, R. O'Shaughnessy. \textit{McFACTS IV: Electromagnetic Counterparts to AGN Disk Embedded Binary Black Hole Mergers}. 2026. arXiv pre-prints, arXiv:2602.04135, (\textit{submitted to the Astrophysical Journal, in review}).

\hangindent=0.5in \noindent B. Mishra, W. Lyra, B. McKernan, M. M. Mac Low, K. E. S. Ford, and \underline{H. E. Cook}. \textit{Active Galactic Nucleus Tori: Potential Birthplace to Millions of Planets}. 2026. The Astrophysical Journal, (\textit{submitted, in review}).

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{AGN Disks as Supernova Mufflers I: 3D Local Hydrodynamic Models}. 2026. arXiv pre-prints, arXiv:2603.29049, (\textit{accepted by the Astrophysical Journal, in press}).

\hangindent=0.5in \noindent V. Delfavero, S. Ray, \underline{H. E. Cook}, K. Nathaniel, B. McKernan, K. E. S. Ford, J. Postiglione, E. McPike, R. O'Shaughnessy. \textit{Prospects for the formation of GW231123 from the AGN channel}. 2026. Physical Review Letters, (\textit{submitted}).

\hangindent=0.5in \noindent \underline{H. E. Cook}, B.~McKernan, K. E. S. Ford, V. Delfavero, K. Nathaniel, J. Postiglione, S. Ray, E. McPike, and R. O'Shaughnessy. \textit{McFACTS II: Mass Ratio--Effective Spin Relationship of Black Hole Mergers in the Active Galactic Nucleus Channel}. 2025. The Astrophysical Journal, 993, 163.

\hangindent=0.5in \noindent  B. McKernan, K. E. S. Ford, \underline{H. E. Cook}, V. Delfavero, E. McPike, K. Nathaniel, J. Postiglione, S. Ray, and R. O'Shaughnessy. \textit{McFACTS I: Testing the LVK AGN Channel with Monte Carlo for AGN Channel Testing and Simulation (McFACTS)}. 2025. The Astrophysical Journal, 990, 217.

\hangindent=0.5in \noindent V. Delfavero, K. E. S. Ford, B.~McKernan, \underline{H. E. Cook}, K. Nathaniel, J. Postiglione, S. Ray, E. Pike, and R. O'Shaughnessy. \textit{McFACTS III: Compact Binary Mergers from Active Galactic Nucleus Disks over an Entire Synthetic Universe}. 2025. The Astrophysical Journal, 989, 67.

\hangindent=0.5in \noindent M. E. Lee, S. Genel, B. D. Wandelt, B. Zhang, A. M. Delgado, S. Pandey, E. T. Lau, C. Carr, \underline{H. Cook}, D. Nagai, D. Angles-Alcazar, F. Villaescusa-Navarro, G. L. Bryan. \textit{Zooming by in the CARPoolGP Lane: New CAMELS-TNG Simulations of Zoomed-in Massive Halos}. 2024. The Astrophysical Journal, 968 11.

\begin{center}
CONFERENCE PROCEEDINGS
\end{center}

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Supernovae Embedded in AGN Disks: And their Light Curves}. Multifrequency Behavior of High Energy Cosmic Sources - XV Workshop. Held 9 -- 14 June 2025. Mondello, Italy. Invited Talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{A Multi-messenger Look at AGN Disk Structure}. American Astronomical Society 245 Winter Meeting. Held 11 -- 16 January 2025. National Harbor, Maryland. Contributed talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Black Hole Merger or Type II Supernova?} Intermediate-Mass Black Holes: The Dawn of A Revolutionary Era. Held 2 -- 5 December 2023. San Pedro, Belize. Contributed talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Fingerprinting the AGN Channel}. Intermediate-Mass Black Holes: The Dawn of A Revolutionary Era. Held 2 -- 5 December 2023. San Pedro, Belize. Contributed poster.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Black Hole Merger or Type II Supernova?} NMSU Graduate Research and Arts Symposium. Held 10 November 2023. Las Cruces, New Mexico. Contributed poster.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Black Hole Merger or Type II  Supernova?} Athena++ Workshop. Held 8 -- 12 May 2023. New York, New York. Contributed poster.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Black Hole Merger or Type II  Supernova?} AGN Santa Fe: Where are the Objects in AGN Disks? Held 22 -- 24 March 2023. Santa Fe, New Mexico. Invited talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Light Curves of Supernovae Embedded in Active Galactic Nucleus Accretion Disks}. 241st Meeting of the American Astronomical Society. Held 9 -- 12 January 2023. Seattle, Washington. Contributed talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Light Curves of Supernovae in Active Galactic Nuclear Accretion Disks}. Intermediate-Mass Black Holes: New Science from Stellar Evolution to Cosmology. Held 30 April -- 3 May, 2022. Puerto Rico. Contributed talk.

\hangindent=0.5in \noindent \underline{H. E. Cook}, W. Lyra, M. M. Mac Low, K. E. S. Ford, and B. McKernan. \textit{Supernovae in AGN Disks: Observability and Structural Impact}. European Astronomical Society 2020 Annual Meeting. Virtual. Held 29 June -- 03 July, 2020. Poster. Abstract SS20: Supernova host environments. id.1168.


% \begin{center}
% Invited Talks, Seminars, \& Colloquia
% \end{center}

\begin{center}
WORKSHOPS
\end{center}

\hangindent=0.5in \noindent \textit{American Astronomical Society Equity-Minded Mentoring workshop}, Attended Apr. 2025

\hangindent=0.5in \noindent \textit{NMSU School Life and Balance workshop}, Attended Mar. 2024

\hangindent=0.5in \noindent \textit{NMSU How to be a Good Mentee workshop}, Attended Feb. 2024

\hangindent=0.5in \noindent \textit{Center for Computational Astrophysics - Computational Fluid Dynamics Summer School}, Attended Aug. 2023

\hangindent=0.5in \noindent \textit{Athena++ User and Developer Meeting}, Attended May 2023

\hangindent=0.5in \noindent \textit{Space Telescope Science Institute Day of Accessibility Workshop}, Attended Apr. 2023


% \pagebreak

\begin{center}
AWARDS AND GRANTS
\end{center}

\noindent A portion of this work was funded by National Science Foundation grant AST-2206096. 

\begin{flushleft}
\begin{tabular}{ll}
2026 & NMSU Spring Semester Graduate Assistantship Award \\
2024 & NMSU Astronomy Zia Award for excellence in research \\
2022--2023 & NMSU Graduate School Outstanding Graduate Assistant Award \\
2022 & NMSU Astronomy Rappaport Award for exceptional public \\
     & outreach and service \\ 
2019--2021 & NMSU Astronomy William Webber Voyager Graduate Fellowship \\
2019--2020 & NMSU Astronomy Pegasus Award for excellence in teaching \\
\end{tabular}
\end{flushleft}

\medskip

\doublespacing
\begin{center}
PROFESSIONAL ORGANIZATIONS
\end{center}
\begin{flushleft}
\begin{tabular}{l}
American Astronomical Society \\
\end{tabular}
\end{flushleft}

\begin{center}
LEADERSHIP AND PROFESSIONAL EXPERIENCE
\end{center}
\begin{flushleft}
\begin{tabular}{ll}
2021--2025 & Co-founder and Manager, Friendly Mentoring In Astronomy \\
           & (FRIENDS) undergraduate peer mentoring program \\
2021--2022 & Financial Officer, Astronomy Graduate Student Organization \\
2020--2021 & Graduate Student Council Representative, Astronomy Graduate \\
	   & Student Organization \\
2020--2021 & Elected Member of Tuition Remission Task Force, Graduate \\
           & Student Council \\
2020 Spring & Tombaugh Observatory Manager, Astronomy Department \\
\end{tabular}
\end{flushleft}
